### 2019-02-26 results.tex
chandras pass

\subsection{Benchmark Applications and Training/Testing  Datasets}
The machine learning applications that we use to evaluate Seneca 
are shown in Table~\ref{tab:bmarks}, each with 
a brief description.
Prophet~\cite{ref:prophet} is a time series analysis library built and maintained by Facebook and the open-source community. The input dataset is a time series of view counts
%logorithm
of Peyton Manning's Wikipedia page from Dec. 10th, 2007 to Jan. 20th, 2016. 
The dataset exhibits both seasonality and a holiday effect (e.g. around the super bowl games). 
We use the first 6 years as the training set and the last 2 years as the testing set.
We use a cross-validation horizon (sliding window) of 1-year, 
and a period (sliding pace) 
of 180 days.  As such, Seneca performs three cross-validations for each 2-year testing range.

@@

Multi-Regression is a regression application developed as part of
an Internet-of-Things (IoT) project~\cite{iot-cpu} (and extended
from linear regression described in the citation, 
to multiple linear regression by the authors of this prior work).
The application predicts outdoor temperature from the processor 
temperature of single board computers (SBCs).  
The technique uses multiple linear regression models computed from time
series of processor temperature measurements,
to predict outdoor microclimate temperatures. % without using a temperature sensor.
%(e.g. for use in 
%precision agriculture applications such as irrigation control and frost protection).
The training dataset consists of eight input time series (one per SBC, each containing 
5-minute measurements) from April 5th, 2018 to Dec. 10th, 2018.

A hyperparameter configuration for this application is a subset of input SBC time series.
Seneca considers all \texttt{$2^N - 1$} potential subsets (for $N$ input time series).
For this application,
we assume the default parameterization is the full set of input time series (8 in this case).
The test dataset for this application is a time series of the outdoor temperature (ground truth) 
over the same period.  The application makes predictions for each of these outdoor temperatures
using the regression coefficients constructed from the training set
and computes the mean square error between predicted and ground truth value pairs.

XGBoost~\cite{ref:xgboost-web} is an open source framework for gradient boosting, which 
performs both regression and classification. We consider it a regression application and
a classification application in this evaluation.  
The hyperparameters and their defaults that Seneca uses in this study are listed in Table~\ref{tab:xgboost_para}. A definition for each hyperparameter can be found in~\cite{ref:xgboostparams}.
%xgboostparams: https://xgboost.readthedocs.io/en/latest/python/python_api.html#module-xgboost.sklearn

Support vector classification (SVC)~\cite{ref:svc} is a classification algorithm 
based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
The hyperparameters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found in~\cite{ref:svcparams}.
%xvcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html

@@

For the classification applications (XGBoost, SVC, and NN), we use a labeled
dataset for training, testing, and evaluation from an IoT 
project~\cite{blind}. The dataset contains measurements from individual
citrus fruit (e.g. oranges, mandarins, lemons, etc.) taken by a fruit sorting
and grading device (using a large number of sensors).  The measurements (i.e.
features) include size, shape, weight, color, diameter, flatness, among other
characteristics, for each fruit.  
The dataset has been filtered to remove correlated
features (those with an absolute value of the Pearson correlation coefficient
greater than 0.8). The dataset has also been balanced by down-sampling and the resulting 
dataset contains 33926 rows (individual fruit) distributed evenly to 5 targets and each row has
18 features.  The label indicates which field the individual fruit was harvested from.  
The application trains a model on a subset (80\%) of the
data.  They then use this model to predict the field
from which each fruit originates (for the remaining 20\%).

The classification applications compute a classification accuracy score
as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
prediction class, $Y_i$ is the true class, $n$ is the number of samples, and 1(x)
is the indicator function. XGBoost also computes MSE for its regression task
on the same datasets.

@@

To evaluate Seneca, we measure tuning performance, application execution time and memory use,
and monetary cost.  For tuning performance, we use mean squared error (MSE)
for regression tasks and percentage accuracy for classification tasks (i.e. we score
model prediction accuracy and not explanatory power).  Because we use the same 
total number of hyperparameters for each model, the penalty function in terms of 
Bayesian Information Criteria, is the same. Thus, we can compare models using
this score.

The default configuration that we consider for each application is described
above.  We report results for the default, best (Seneca's recommendation), and
worst performing configurations.  Seneca computes all possible combinations of
the hyperparameter settings specified in the configuration to extract each of
these results.  The default results represents those that a novice or first
time user might employ when using these applications as a ``black box.''  The
worst performing scenario shows how bad the results can be when parameters are
poorly tuned.  Finally, the best is the upper bound on what is possible from
tuning the hyperparameters for the values and dataset specified 
(e.g. using expert knowledge or Seneca).

To evaluate the cost savings introduced by Seneca, we deploy the applications
on Amazon Web Services (AWS) Lambda~\cite{ref:awslambda} and extract
execution time and memory use from AWS CloudWatch~\cite{ref:awscloudwatch} logs.  
We then compute monetary cost
using the AWS Lambda pricing model~\cite{ref:pricing}.
%awslambdapricing: https://aws.amazon.com/lambda/pricing/
Each function downloads the training and testing dataset 
of the application from AWS Simple Storage Service (S3)~\cite{ref:awss3} upon function invocation. 
We do not consider the cost of dataset storage in our cost computations (it is very small).

%We also experiment with different memory configurations for Seneca functions
%in AWS Lambda.  
We also investigate Seneca's automatic memory optimization capabilities.  To
do so we compare the execution performance and cost of the benchmarks using
the maximum allocatable memory size to the performance and cost when run with
Seneca's automatically determined memory size. Though memory size used reported by AWS CloudWatch fluctuates throughout the tuning process, we have verified the optimized allocated memory allows all hyperparameter settings run successfully.

@@

Figure~\ref{fig:box_plot_mse} provides a box plot of MSE (lower is better) for
these applications for the entire hyperparameter search space. The central
rectangle covers the interquartile range (IQR), which is defined as the range
of data points from first quartile to third quartile (Q3 - Q1).  The upper
whisker extends to the last datum less than \texttt{$(Q3 + 2 * IQR)$} and the
lower whisker extends to the first datum greater than \texttt{$(Q1 - 2 *
IQR)$}. The data points beyond the whiskers are considered outliers and are
plotted as colored diamonds. The red notch identifies the MSE that results
from training the model using the default settings of hyperparameter. The
difference between red notch of lowest data point is improvement brought about
through the use of Seneca. From the location of red notch, we can see the MSE
metrics from default configuration in three applications are close to the
first quartile value in all three cases (slightly greater that Q1 for Prophet
and Multi-regression and slight less for XGBoost). However, Seneca's MSE
performance is congruent with the end of the lower whisker.  Overall, however,
the quality of the application's output (for a given dataset) is dramatically
affected by hyperparameter settings.  Predictably the default settings are
near the ``good'' end of the spectrum, but as both Table~\ref{tab:mse} and
Figure~\ref{fig:box_plot_mse} indicate, Seneca is able to find
parameterization that improves output quality over the default settings
in each case.
%Thus for Prophet
%and Multi-Regression, Seneca 
%, meaning the potential room for improvement is about 75\%
%over the range of MSE metric. The box plot also illustrates that the best MSE
%of Prophet and multivariate regression are among outliers, where a
%comprehensive search is very critical to find the best configurations. 
%\textcolor{blue}{Add more analysis here to discuss the variance in the MSE
%for the range of configurations and how they change across applications.
%Include any insights that the boxplots add.}

@@

The 80-20 case represents the typical usage of these classification
applications. Often, when evaluating the accuracy of a specific classifier,
the user uses the 80-20 split ``rule'' when measuring accuracy. In this case,
Seneca's improvement over the default parameterizations varies from 2.46\% for XGBoost application (column 2), to 19.04\% for SVC
(column 3).

@@

Figure~\ref{fig:box_plot_accuracy} presents the accuracy (higher is better) 
for the entire hyperparameter search space for each classification
application.  The central rectangle covers from first quartile to third quartile (Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}. The red notch indicates the accuracy metric from the model trained by default settings and colored diamonds are outliers beyond whiskers.
For both types of applications (regression and classification), Seneca significantly
improves tuning performance over the default and worst case configurations for SVC while generating a relatively small improvement over the default for XGBoost and Neural Network. This is because powerful classifiers, like XGBoost and Neural Network, can achieve fairly good accuracy by default setting, whereas weaker classifier, like SVC, requires more tuning to reach high accuracy.

\begin{table}[t]
\centering
\scriptsize
\input{tables/exec-time-memory-tab}
\caption{The mean (stdev) values of execution time and memory use, and best accuracy across 30 executions of three classification benchmarks running against two random states. It verifies data split does not have major impact to execution metrics and scores.
\label{tab:exec_memory}}
%\vspace{-0.2in}
\end{table}

In order to investigate the potential impact from data split, we split the data for three classification applications by two random states, run Seneca 30 times and obtain execution time, memory use and best accuracy from AWS CloudWatch logs. As showed in Table~\ref{tab:exec_memory}, different data split has no major impact to these three values. It does not only mean the execution time and monetary cost are consistent given various data splits, but also indicates users do not have to run Seneca repetitively in the inference phase when new data are generated.

@@

Finally in this section, we contrast the execution time of Seneca with serial hyperparameter tuning process on EC2 instance across five applications. Since library compilation issue, we use t2.medium on Prophet and t2.micro on other 4 applications. As a result, Seneca achieves at least 4x speedup for IO-bound application (SVC) and 21x speedup for CPU-bound application (XGBoost). It confirms Seneca can execute tuning within a more reasonable period of time, comparing to executing serially on EC2 instance.

@@

% To do so, we use Seneca to find the hyperparameterization that optimizes application output
% quality (lowest MSE for regression, highest accuracy for classification).
% For each hyperparameterization that Seneca evaluates, it incurs a
% cost. Furthermore, the amount of memory used by Seneca during memory
% tuning also influences overall cost.

We next analyze the monetary costs incurred by Seneca. Instead of trying out all possible settings,  we compare two
Seneca execution configurations.  In the first 
we configure each lambda function to
use the maximum amount of memory allowed by AWS Lambda (3008 MB) for all
executions.
Second, we employ Seneca's memory optimization which automatically detects and configures
the amount of memory needed by each function.  This optimization requires
Seneca to ``probe'' to determine the best memory size to use.  The
cost of these probes
(denoted ``Optimizer Cost'') must be taken into account as well.
%Because memory impacts both
%cost and execution time (total latency of Seneca hyperparameter tuning), we
%present empirically evaluate both in this subsection.  
Note that XGBoost's performance profile is identical when used for regression
or classification so we include its measurements only once in the following
analysis.
%For each, we only
%include XGBoost once since its performance profile is the same regardless of
%whether we are using regression or classification.

Tables~\ref{tab:cost_optimized} shows the results with and without 
the Seneca memory optimization, respectively. The five columns identify the benchmark applications and the first row is the total execution time in minutes and the second row is total cost of tuning when Seneca's lambda functions are configured to use the maximum amount of memory (3008 MB). For optmized memory configuration, fourth row shows the cost of the memory optimizer in the
second row, Seneca's cost using the optimization in the fifth row, and total cost on sixth row.
Finally, in the seventh and eighth rows of Table~\ref{tab:cost_optimized} we show the
savings that memory optimization introduces over using the maximum memory in dollar cost and as a percentage respectively.

\begin{table}
\centering
\input{tables/seneca-mem-opt-tab.tex}
\caption{Seneca Memory Optimization: First two rows show the execution time and  monetary cost of using Seneca at max memory (3008 MB). Row 3-6 show the execution time and cost when the amount of memory used for each function invocation is automatically inferred and set by Seneca. Row 7-8 show savings by dollar and percentage.
\label{tab:cost_optimized}}
\vspace{-0.2in}
\end{table}

Table~\ref{tab:cost_optimized} illustrates two important cost features of Seneca.  First, using
AWS Lambda, full hyperparameter space exploration is not expensive in 
\textit{absolute} dollar cost terms.  Even using the maximum memory available
for almost 25 minutes of execution time (cf Prophet in Table~\ref{tab:cost_optimized}), the
total dollar cost is approximately 73 cents.  Secondly, Seneca's memory
optimizations produce a significant percentage savings which, over repeated
executions, is important.

Note also that Seneca's memory/cost optimization
introduces at an execution time penalty (relative to the maximum memory
execution) for some of the applications.  That is, the
execution times for all applications increase when Seneca chooses
a memory size.  Thus while Seneca is finding the best application output
quality and optimizing the cost of producing that output, it is doing so at
the expense of execution performance (time to solution). Such a penalty
is expected due to the proportional CPU power to allocated
memory. However, the Seneca optimizer is able to find the optimal
memory configuration to minimize that  penalty. In the case of SVC, Seneca saves 30\% compared to max memory execution (\$0.016 vs \$0.023) but has almost the same execution time (1.91 vs 1.95 minutes).
% The source of this execution performance penalty is not clear.  We hypothesize
% that when requesting a large memory for AWS Lambda, Amazon chooses a machine
% that also has fast processors so the Lambda functions execute more quickly.
% If this supposition is true, then the AWS Lambda pricing model correctly
% weights the cost of additional memory (in light of the reduced execution time)
% because the large-memory executions are still more expensive.
%However regardless of the cause, 
Even in the worst case of CPU-bound application, the Seneca memory optimizer still provides a way to trade off time to solution for cost when the highest possible application output quality is desired.

To corroborate the cost-effectiveness of Seneca, we analyzed the total cost of five benchmarks in 30 executions from last section. We observe the reported \textit{billed duration} and \textit{max memory used} oscillate that leads to different total cost across 30 executions and we assume it is because the pagination and memory sampling method used by different AWS Lambda host servers. However, even taking fluctuation into account, the highest cost of execution under optimized memory is still cheaper than the lowest cost of execution under maximum memory in all five benchmarks. We believe Seneca's optimizer is economical despite the locality of lambda container and application.

>>>>

\subsection{Benchmark Applications and Training/Testing  Datasets}
The machine learning applications that we use to evaluate Seneca 
are shown in Table~\ref{tab:bmarks}, each with 
a brief description.  Prophet, Multi-Regression, and XGBoost are regression
applications; XGBoost, SVC, and NN are classification applications (XGBoost 
implements both regression and classification tasks).

Prophet~\cite{ref:prophet} is a time series analysis library built and maintained by Facebook and the open-source community. The input dataset is a time series of view counts
%logorithm
of Peyton Manning's Wikipedia page from Dec. 10th, 2007 to Jan. 20th, 2016. 
The dataset exhibits both seasonality and a holiday effect (e.g. around 
super bowl games). 
We use the first 6 years as the training set and the last 2 years as the testing set.  We use a cross-validation horizon (sliding window) of 1-year, 
and a period (sliding pace) 
of 180 days.  As such, Seneca performs three cross-validations for each 2-year test range.

@@

Multi-Regression is a regression application developed as part of
an Internet-of-Things (IoT) project~\cite{iot-cpu} (which has been
extended from linear regression described in the citation 
to multiple linear regression by the authors of this prior work).
The application predicts outdoor temperature from the processor 
temperature of single board computers (SBCs).  
The technique uses multiple linear regression models computed from time
series of processor temperature measurements,
to predict outdoor microclimate temperatures. 
The training dataset consists of eight input time 
series (one per SBC, each containing 
5-minute measurements) from April 5th, 2018 to Dec. 10th, 2018.

A hyperparameter configuration for this application is 
a subset of input SBC time series.
Seneca considers all \texttt{$2^N - 1$} potential subsets (for $N$ input time series).
For this application,
we assume the default parameterization is the 
full set of input time series (8 in this case).
The test dataset for this application is a time 
series of the outdoor temperature (ground truth) 
over the same period.  The application makes 
predictions for each of these outdoor temperatures
using the regression coefficients constructed from the training set
and computes and returns the MSE between predicted 
and ground truth value pairs.

XGBoost~\cite{ref:xgboost-web} is an open source 
framework for gradient boosting, which 
performs both regression and classification. 
The hyperparameters and the default values that Seneca uses 
in this study are listed in Table~\ref{tab:xgboost_para}. 
A definition for each hyperparameter can be found in~\cite{ref:xgboostparams}.
%xgboostparams: https://xgboost.readthedocs.io/en/latest/python/python_api.html#module-xgboost.sklearn

Support vector classification (SVC)~\cite{ref:svc} 
is an implementation of a classification algorithm 
that is based on support vector machines that is part of the
libsvm~\cite{ref:libsvm} library.
The hyperparameters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found in
%svcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html
\footnote{\url{https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html}}.

@@

For the classification applications (XGBoost, SVC, and NN), we use a labeled
dataset for training, testing, and evaluation from an IoT 
project~\cite{blind}. The dataset contains measurements from individual
citrus fruit (e.g. oranges, mandarins, lemons, etc.) taken by a fruit sorting
and grading device (using a large number of sensors).  The measurements (i.e.
features) include size, shape, weight, color, diameter, flatness, among other
characteristics, for each fruit.  
The dataset has been filtered to remove correlated
features (those with an absolute value of the Pearson correlation coefficient
greater than 0.8). The dataset has also been balanced by 
down-sampling and the resulting 
dataset contains 33926 rows (individual fruit) 
distributed evenly across 5 targets. Each row has
18 features.  The label identifies the field from which the 
individual fruit was harvested.

The applications train a model on a subset (80\%) of the
data.  Each then uses this model to predict the field
from which each fruit originates (for the remaining 20\%). 
The applications compute a classification accuracy score
as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
prediction class, $Y_i$ is the true class, 
$n$ is the number of samples, and 1(x)
is the indicator function. The applications return the accuracy percentage
upon completion. As mentioned above, in addition to returning
classification accuracy for its classification task, XGBoost also returns 
MSE for its regression task.

@@

To evaluate Seneca, we measure tuning performance, application execution time, 
memory use, and monetary cost.  For tuning performance, 
we use mean squared error (MSE)
for regression tasks and percentage accuracy for classification 
tasks (i.e. we score model prediction accuracy and not explanatory power).  
Seneca is able to compare models for each type of application using 
these scores because it uses the same
total number of hyperparameters for each model.  Thus, the
the penalty function in terms of 
Bayesian Information Criteria is the same.

The default configuration that we consider for each application is described
above.  We report results for the default, best (Seneca's recommendation), and
worst performing hyperparameter configurations for each application type.  
Seneca computes all possible combinations of
the hyperparameter settings specified in the configuration to extract each of
these results.  The default results represents those that a novice or first
time user might employ when using these applications as a ``black box.''  The
worst performing scenario shows how bad the results can be when parameters are
poorly tuned.  Finally, the best is the upper bound on what is possible from
tuning the hyperparameters for the values and dataset specified 
(e.g. using expert knowledge or Seneca).

To evaluate the  savings introduced by Seneca, we deploy the applications
on Amazon Web Services (AWS) Lambda and extract
execution time and memory use from AWS CloudWatch~\cite{ref:awscloudwatch} logs.  
Seneca extracts execution time and memory use from AWS CloudWatch logs\footnote{\url{https://aws.amazon.com/cloudwatch/}}.
We compute monetary cost
using the AWS Lambda pricing model\footnote{\url{https://aws.amazon.com/lambda/pricing/}}.
%awslambdapricing: https://aws.amazon.com/lambda/pricing/
Each function downloads the training and testing dataset 
of the application from AWS S3 upon function invocation. 
We do not consider the cost of dataset storage 
in our cost computations (it is very small).

%We also experiment with different memory configurations for Seneca functions
%in AWS Lambda.  
We also investigate Seneca's automatic memory optimization capabilities.  To
do so we compare the execution performance and cost of the benchmarks using
the maximum allocatable memory size to the performance and cost when run with
Seneca's automatically determined memory size. Though memory size used reported by AWS CloudWatch fluctuates throughout the tuning process, we 
have verified that the optimized allocated memory is sufficient for all 
hyperparameter configurations to complete successfully.

@@

Figure~\ref{fig:box_plot_mse} provides a box plot of MSE (lower is better) for
these applications for the entire hyperparameter search space. The central
rectangle covers the interquartile range (IQR), which is defined as the range
of data points from first quartile to third quartile (Q3 - Q1).  The upper
whisker extends to the last datum less than \texttt{$(Q3 + 2 * IQR)$} and the
lower whisker extends to the first datum greater than \texttt{$(Q1 - 2 *
IQR)$}. The data points beyond the whiskers are considered outliers and are
plotted as colored diamonds.

The red notch identifies the MSE that results
from training the model using the default settings of hyperparameter. The
difference between red notch of lowest data point is improvement brought about
through the use of Seneca. From the location of red notch, we can see the MSE
metrics from default configuration in three applications are similar to those
in the first quartile for all applications.
This data shows that the quality of the
output generated by each application (for a given dataset) is dramatically
affected by hyperparameter settings.  Predictably, the default settings are
near the ``good'' end of the spectrum, but as both Table~\ref{tab:mse} and
Figure~\ref{fig:box_plot_mse} indicate, Seneca is able to find
parameterization that improves output quality over the default settings
in each case.
%Thus for Prophet
%and Multi-Regression, Seneca 
%, meaning the potential room for improvement is about 75\%
%over the range of MSE metric. The box plot also illustrates that the best MSE
%of Prophet and multivariate regression are among outliers, where a
%comprehensive search is very critical to find the best configurations. 
%\textcolor{blue}{Add more analysis here to discuss the variance in the MSE
%for the range of configurations and how they change across applications.
%Include any insights that the boxplots add.}

@@

%not sure what this paragraph is adding, seems to a repetition of what
%is already said above...
%The 80-20 case represents the typical usage of these classification
%applications. Often, when evaluating the accuracy of a specific classifier,
%the user uses the 80-20 split ``rule'' when measuring accuracy. In this case,
%Seneca's improvement over the default parameterizations varies from 2.46\% for XGBoost application (column 2), to 19.04\% for SVC
%(column 3).

@@

Figure~\ref{fig:box_plot_accuracy} presents the accuracy (higher is better) 
for the entire hyperparameter search space as a box plot for each classification
application.  The placement of the rectangle and whiskers is the same
as in Figure~\ref{fig:box_plot_mse}. 
%The central rectangle covers from first quartile to third quartile (Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}. 
The red notch indicates the accuracy metric from the model trained by default settings and colored diamonds are outliers beyond whiskers.
Again, Seneca significantly
improves tuning performance over the default and worst case configurations for SVC while generating a smaller improvement for XGBoost and Neural Network versus the default.
This is because XGBoost and NN use a well tuned default parameter
set that works well for most datasets.  SVC benefits more from Seneca tuning
that the others.

\begin{table}[t]
\centering
\scriptsize
\input{tables/exec-time-memory-tab}
\caption{The mean and standard deviation (in parentheses) values of execution time and memory use, and best accuracy across 30 executions of three classification benchmarks running against two random states. It verifies data split does not have major impact to execution metrics and scores.
\label{tab:exec_memory}}
%\vspace{-0.2in}
\end{table}

To investigate the potential impact of the 80-20 data split for the classification
applications, we next evaluate the quality of the output generated from 
each when we consider different 80-20 random splits.
To enable this, we run Seneca 30 times to obtain execution time, memory use, 
and best accuracy score. 
Table~\ref{tab:exec_memory} shows the mean and standard deviation of these 
metrics across runs for two different random splits.  The Seneca score
is similar across splits.  As a result, users can employ the models
(for the selected hyperparameter settings) that Seneca recommends
repeatedly for inference to amortize the cost of using Seneca.

@@

Finally, we compare Seneca to AWS EC2 use.
We measure the execution time of Seneca and hyperparameter tuning 
using the least expensive EC2 instance type in which the application
will run (t2.micro for SVC and NN, t1.medium for the rest).  End to end, Seneca's
concurrency facilitates in a 4x -- 17x (9x on average) speedup
and \$0.01--\$0.34 (\$0.13) additional cost over serialized execution in EC2.
EC2 trades off monetary cost for programmer productivity, i.e. the developer 
must setup, deploy, and manage the applications manually. Moreover, the EC2
pricing model is imposed on hour boundaries. Moreover, Seneca and 
AWS Lambda impose no cost when no execution is occuring (EC2 instances must
stay idle in between runs). As part of future work, we will compare Seneca
to the AWS Elastic Container Service.
%\textcolor{blue}{FIX THIS: State the results (speed up) per application and 
%also state the cost analysis for 1 hour of computation.  Clarify that this
%is due to the 1-hour pricing model of EC2.}

%We use instance type t2.medium
%for Prophet (since it cannot be built
%process on EC2 instance across five applications. Since library compilation issue, we use t2.medium on Prophet and t2.micro on other 4 applications. 
%As a result, Seneca achieves at least 4x speedup for IO-bound application (SVC) and 21x speedup for CPU-bound application (XGBoost). It confirms Seneca can execute tuning within a more reasonable period of time, comparing to executing serially on EC2 instance.

@@

We next analyze the monetary cost incurred by Seneca with and without 
Seneca's memory optimization.
We consider the use of the maximum allocatable memory (3GB) and Seneca's 
automatic detection and configuration of allocated memory.
This optimization requires
that Seneca intelligently probe to determine the best memory size 
to use.  We report the cost of these probes as \texttt{Optimizer Cost}.

Table~\ref{tab:cost_optimized} shows the results with and without
the Seneca memory optimization. 
The five columns identify the benchmark applications.
Because the performance profile of XGBoost is the same for regression
or classification, we include its metrics once.
The first two rows show the results when we use the maximum allocated memory 
for the Lambda functions. We present execution time in minutes (row 1) and 
monetary cost (row 2).

Rows 3--6 show the performance and cost impact of using Seneca's memory optimization.
is the execution time in minutes 
\texttt{Exec time opt} is the execution time in minutes.
\texttt{Optimizer Cost} is monetary cost of Seneca's memory size detector.
\texttt{Cost opt} is monetary cost of using Seneca and the memory size
it identifies and recommends.
\texttt{Total cost} is the sum of \texttt{Optimizer Cost} and \texttt{Cost opt}, i.e., the total cost of using Seneca to perform hyperparameter tuning for these applications and data sets.
The last two rows show the monetary savings (row 7) and percent savings (row 8) u
of using Seneca's memory optimization.  Seneca's memory optimization reduces
the monetary cost of its use from 10--30\% (20\% on average).

\begin{table}
\centering
\input{tables/seneca-mem-opt-tab.tex}
\caption{Seneca Memory Optimization: Rows 1--2 show the execution time and  monetary cost of using Seneca without its memory optimization. Rows 3-6 is the execution time and cost, respectively, when Seneca detects and sets allocated memory for the application functions automatically.  Rows 7-8 show the savings by dollar and percentage.
\label{tab:cost_optimized}}
\vspace{-0.2in}
\end{table}

Table~\ref{tab:cost_optimized} illustrates two important points.
First, using AWS Lambda, full hyperparameter space exploration is not expensive in 
\textit{absolute} dollar cost terms and Seneca's automatic memory size optimization
decreases this cost further.  Second, this optimization reduces cost but can 
increase the total execution time for parameter search 
since the functions must operate under additional memory 
constraints (versus using the maximum allocated memory).  
In addition, this cost fluctuates depending on the quality of the Lambda
execution environment (number of CPUs, Linux container overhead, 
multitenency, etc.).  We omit the data due to space constraints.
However, the average absolute difference in cost
across the five applications (30 runs) is \$0.050. %I use only split 1 for all 5
%numbers are below
Moreover, the highest cost of execution under 
optimized memory is still cheaper than the lowest cost of execution 
under maximum memory for all five benchmarks.  
%$	Ave Cost	Highest Cost	Lowest Cost	Diff (High - low)
%Prophet	0.215	0.294	0.178	0.116
%Multi_Reg	0.076	0.078	0.075	0.003
%SVC_1	0.015	0.015	0.015	0.001
%SVC_2	0.014	0.016	0.013	0.003
%XGBoost_1	0.586	0.632	0.510	0.122
%XGBoost_2	0.607	0.630	0.569	0.061
%NN_1	0.055	0.059	0.051	0.007
%NN_2	0.058	0.061	0.056	0.005

Overall, given the AWS Lambda cost model and its performance variability, 
Seneca is still able to find the sweet spot between cost 
and execution time. Thus Seneca can be used to trade off time-to-solution for
cost as desired by users.

%Even using the maximum memory available
%for almost 25 minutes of execution 
%time (cf Prophet in Table~\ref{tab:cost_optimized}), the
%total dollar cost is approximately 73 cents.  Secondly, Seneca's memory
%optimizations produce a significant savings to further reduce its cost.
%
%Note that Seneca's memory/cost optimization
%can introduce an execution time penalty (relative to the maximum memory
%execution) for some of the applications.  
%That is, the
%execution times for all applications increase when Seneca chooses
%a memory size.  Thus while Seneca is finding the best application output
%quality and optimizing the cost of producing that output, it is doing so at
%the expense of execution performance (time to solution). Such a penalty
%is expected due to the proportional CPU power to allocated
%memory. However, the Seneca optimizer is able to find the optimal
%memory configuration to minimize that  penalty. In the case of SVC, Seneca saves 30\% compared to max memory execution (\$0.016 vs \$0.023) but has almost the same execution time (1.91 vs 1.95 minutes).
% The source of this execution performance penalty is not clear.  We hypothesize
% that when requesting a large memory for AWS Lambda, Amazon chooses a machine
% that also has fast processors so the Lambda functions execute more quickly.
% If this supposition is true, then the AWS Lambda pricing model correctly
% weights the cost of additional memory (in light of the reduced execution time)
% because the large-memory executions are still more expensive.
%However regardless of the cause, 
%Even in the worst case of CPU-bound application, the Seneca memory optimizer still provides a way to trade off time to solution for cost when the highest possible application output quality is desired.

%To corroborate the cost-effectiveness of Seneca, we analyzed the total cost of five benchmarks in 30 executions from last section. We observe the reported \textit{billed duration} and \textit{max memory used} oscillate that leads to different total cost across 30 executions and we assume it is because the pagination and memory sampling method used by different AWS Lambda host servers. However, even taking fluctuation into account, the 
%highest cost of execution under optimized memory is still cheaper than the lowest cost of execution under maximum memory in all five benchmarks. We believe Seneca's optimizer is economical despite the locality of lambda container and application.
